A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Move "non-goal" paragraph into subsubsection and clarify.

Although other researchers construct supertrees for the purpose of
inferring the true tree from the input trees \citep{BinindaEmonds2007b,Davis2014},
we note that phylogeny estimation is an explicit non-goal of our
supertree method.  We do not treat input trees as data or as surrogates for
data matrices \citep{gatesy2004critique}, and we do not claim that our
summary supertree is more accurate than the input trees because more
data lies behind it. Instead we seek to \emph{summarize and represent}
the input trees, even when they conflict with each other.  The
annotations file constructed by our pipeline is essential for this
task because it includes information about conflict with our supertree
as well as support for it.

@@

>>>>

@@

\subsubsection{Non-goal: phylogeny estimation}
Many researchers construct supertrees for the purpose of inferring the true tree from the input trees \citep{BinindaEmonds2007b,Davis2014}.  Such approaches treat input trees as data or as surrogates for data matrices \citep{gatesy2004critique}, and the supertree is seen as more accurate than the individual input trees because more input trees (and presumably more data) stand behind it.  For such methods, conflict resolution is a primary aim of the method.

Our supertree method operates in a different paradigm.  Phylogeny estimation is an explicit non-goal of our supertree algorithm.  We do not claim that the supertree is more accurate than the input trees it summarizes, and so conflict resolution is not a primary aim of the method. Most of our input trees have non-overlapping taxon sets, and so conflict resolution is not the primary problem.  Instead, seek to merge and aggregate phylogenetic information on the largest possible scale.  Therefore, the primary aim of our supertree method is to \emph{summarize and represent} the input trees, even when they conflict with each other.  The annotations file constructed by our pipeline is essential output because it includes information about conflict with our supertree as well as support for it.

Our method must resolve conflicts in order to construct a single supertree.  However, the rank information used to resolve conflicts is an input to the method, not an output from the method.  We thus perform curation-based conflict resolution, not inference-based conflict resolution.
